Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-03 doc/report/intro.tex
adding files to the report

So far, our proposal Looks fairly similar to \cite{Merrill:2007:ALP:1758156.1758158}.

>>>>

There has been the vision of smart-home and smart-office where everything around is intelligent enough to assist human in everyday life. The development of radio technology, sensors, and actuators are making this dream come true. You can buy those basic components online \cite{SmartHome, NinjaBlocks} and many hobbyists have already created their own smart environment (see \cite{BRAD} as an example). Recently, with the the prevalence of smartphones, many systems \cite{SmartThings, Lockitron} have been integrated into smartphone applications to lower the barrier for ordinary users.

Admittedly, people have been used to accessing the Internet, conversing with friends, and even dealing with online business through their smartphones. These handheld devices serve as an important portal for users to be connected to the Internet. And now many systems are making smartphones the portal to interact with physicalworld. Given all the benefits we can get by using smartphones -- networking,  display, gesture input, and increasing computability,  we argue that traditional GUI on mobile platform still imposes difficulty in interacting with physical objects. Take iPhone for example, users are required to browse a list of possible icons and then select the right one. Even on Android platform, you can create widget to simplify the browsing overhead. We hold the opinion that squeezing physically distributed objects onto a-few-inch screen is not the right approach. And a more direct approach is desirable.

In this project, we aim to explore the ability of direct interaction by using glass-based attention tracking to pin-point the target.

% explain why we need glass form factor

The rest of this paper is structured as follows. In Sec.\,\ref{sec:related-work}, we will give an overview of some related projects. Then we present our approach in detail about the system design and implementation in Sec.\,\ref{sec:design} and Sec.\,\ref{sec:implementation} respectively. Then Sec.\,\ref{sec:evaluation} shows our evaluation results and we provide an in-depth discussion (Sec.\,\ref{sec:discussion}) about different kinds of interaction since not all are suitable for our system. Sec.\,\ref{sec:conclusion} concludes this paper.

### 2013-05-03 doc/report/main.tex
adding files to the report

\hypersetup{%
pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true,}

@@

\title{Attention Tracker}

@@

% \begin{abstract}

% \end{abstract}

@@

% \terms{Design, Experimentation, Measurement} 
% \keywords{Localization, Magneto-Inductive, Tracking, Virtual Zone}

\input{intro.tex}

>>>>

\hypersetup{%
pdftitle={Project Glass 2.0}, pdfauthor={Ben Zhang, Sean Chen}, pdfkeywords={HCI}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true,}

@@

\title{Project Glass 2.0 -- Interaction with Physical Devices through Attention}

@@

\begin{abstract}
With the increasing interest of assigning intelligence to everyday object, many approaches of interacting with them fall back to smartphone based applications. We argue about the inconvenience, overhead, and distraction in such an interaction paradigm, and propose a more natural solution. A glass-based controller which enables user to express their interest in interaction directly simplifies the process of selection in a smart-home or smart-office senario. We present our thoughts, design and evaluation of such a system in this paper to motivate researchers in considering ``interaction in attention''. In the meantime, we noticed that Google Glass might serve as the perfect enabling technology, though in our prototype we've adopted simple infrared approach for proof-of-concept.
\end{abstract}

@@

% \terms{Design, Experimentation, Measurement} 
\keywords{HCI, Interaction, Attention, Infrared, Glass}

\input{intro.tex}
\input{related.tex}
\input{design.tex}
\input{implementation.tex}
\input{evaluation.tex}
\input{discussion.tex}
\input{conclusion.tex}

### 2013-05-03 doc/report/related.tex
adding files to the report

>>>>

In this section, we will first summarize some prior work and how it relates to our project in three folds: Tangible User Interface (TUI), Glass-based device, and Attention Aware System (AAS), discussing each in turn.

\subsection{Tangible User Interface}
\label{sec:tang-user-interf}

The concept of Tangible User Interface was proposed in \cite{Ishii:1997:TBT:258549.258715}, and according to the original paper, such system would enable user to ``grasp \& manipulate bits in the center of users' attention by coupling the bits with everyday physical objects and architectural surfaces''. Thereafter, numerous TUI systems (such as \cite{Nanayakkara:2012:EEF:2212776.2212382, Patel:2006:IPA:2094945.2094962}) are developed. \cite{Merrill:2007:ALP:1758156.1758158} is one that is closest to our system, which base users' interaction with physical objects on people's natural looking, pointing and reaching metaphor. However, these systems have limitations that they focus too much on sensing the physical world, while the actuation is mostly done in cyber world. Recent years, many startups \cite{SmartThings, NinjaBlocks, Lockitron} tries to ``hack'' the physical world to achieve the envisioned Internet of Things by enabling actuating devices from phone/web portal.

Our system combines some merits from prior work. We also user people's natural looking as attention tracking as in \cite{Merrill:2007:ALP:1758156.1758158}, but we are not limited to browsing or searching physical objects. We provide such capability of interacting directly with physical device, in addition to control with a mobile phone or web portal \cite{SmartThings, NinjaBlocks}.

\subsection{Glass Form-factor}
\label{sec:glass-form-factor}

\cite{mann2004continuous}, as the earliest wearable device, uses the form factor of glass to serve as a logging machine that records user's’ daily life. According to one review paper \cite{morris2010emerging}, there are many glass-based device developed for the past decades. Those who use glasses as input have primarily focused on gaze-tracking \cite{Selker:2001:EGE:634067.634176, Nagamatsu:2010:MDG:1753846.1753983}, and the projects that uses glasses for available output device works hard to achieve virtual reality \cite{Lumus, GoogleGlass}.

The most recent and potentially most impactful project \cite{GoogleGlass} integrate many crucial components -- camera, projection, microphone, speaker, IMU and networking -- into a single glass that can achieve virtual reality to an unimaginable extent. We do believe this might be a powerful platform for future interaction development. However, so far the vision is still being limited to Cyber world. Our project explores the potential of using glasses for direct interacting with physical devices, rather than doing ``digital'' tasks.

\subsection{Attention Aware System}
\label{sec:attent-aware-syst}

Microsoft Research's project ``Attentional User Interface'' \cite{horvitz2003models} explores how attention can be employed to enhance human-computer interaction, from the lesson learned in human-human interaction. Attention detection can also assist interface design to avoid context shifting overhead, e.g. the peripheral displays and the notification level should be adjusted according to user's attention \cite{parkdesigning}.

Our work also borrows ideas from these project in that we seek to identify users' attention to select the right physical object to interact.
